---
title: "MTCars"
format: html
editor: visual
---

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973--74 models).

To learn more about the data, see here: https://www.rdocumentation.org/packages/datasets/versions/3.6.2/topics/mtcars

```{r}
data("mtcars")
View(mtcars)
```

1. Create a code chunk and run the *summary* command on a single quantitative varable in the dataset mtcars.

2. Fill in the following code (replace the ... below) to create a histogram of the quantitative variable you selected in question 1. 

```{r}

ggplot(mtcars, aes(x= ...)) + geom_histogram()
```

Did it work? If not, you may need to library the ggplot package. do that in the code above!

3. That histogram is really boring.... fill in your same x and give it an informative title by filling the " " below. 

```{r}
ggplot(mtcars, aes(x= ... )) + geom_histogram() + labs(title=" ")
```


4. Let's explore if cars with or without a transmission get better mpg. Put am in the space for color and fill and run the code. Continue to put your variable in x = and write out a title. 
```{r}
mtcars$am <- as.factor(mtcars$am) #This makes sure am is a factor

ggplot(mtcars, aes(x= ... , color = ... , fill = ... )) + geom_histogram() + labs(title=" ")

```

5. Let's add a density curve. Run the following code below. Play around with alpha and see how the graph changes.

```{r}
ggplot(mtcars, aes(x= mpg , color = am , fill = am )) + geom_histogram(aes(y=..density..), position="identity") + labs(title="MPG") +
geom_density(alpha=0.6)
```

6. Let's rip the histogram apart and seperate by the variable am. Fill in your quantitative variable in x = and put your transmission variable in the ... after facet_grid. 

```{r}
ggplot(mtcars, aes(x= ...))+
  geom_histogram(color="black", fill="white")+
  facet_grid(... ~ .)
```



7. For additional practice with the MT data set, please click [here](https://www.statology.org/mtcars-dataset-r/)